Death By Dropdown?

### 2025-04-04 conference-materials/2025_shiny-conf/slides.qmd
Refines slide 6 layout
- Improves visual organization of slide 6 by switching to callout with title and putting into right column

::: {.column}
- **UX Design**: Beyond heuristic lists to guided process
- **Data Storytelling**: From data dumps to meaningful narratives
:::

::: {.column}
- **Psychological Science**: Evidence-based cognitive principles
- **Visual Communication**: Optimized for information perception
:::

@@

::: {.callout-note .mt-3}
**Key Differentiator**: Process-oriented framework vs. typical checklist approach
:::

>>>>

:::: {.columns .absolute top="50%" .r-fit-text}

::: {.column .fragment }
- **UX Design**: Established best practices
- **Data Storytelling**: From data dumps to meaningful narratives
- **Psychological Science**: Evidence-based cognitive principles
- **Visual Communication**: Optimized for information perception
:::

::: {.column .callout-tip .fragment}
### Key Differentiator

Process-oriented framework vs. broad checklist approach
:::

@@
